\begin{frame}

\vspace{\fill}

\begin{center}

\Large


\textbf{Why Would You Write a Report?} \\[2em]

Discussion

\end{center}

\vspace{\fill}

\end{frame}

\begin{frame}

\frametitle{What Should Be Clear From Your Report}

(Without looking at your code!)

\vspace{\fill}

\begin{enumerate}

\item In-how-far you have solved a given task

\item In-how-far you have tested your solution

\item How to compile and run your code (if possible)

\item How to reproduce your test results

\end{enumerate}

\vspace{\fill}

\end{frame}


\begin{frame}

\frametitle{What Should Your Report Add?}

(Besides what is clear from your code!)

\vspace{\fill}

\begin{enumerate}

\item Give an overview of your code

\item Justify your design decisions;\\ contrast with other possible
solutions

\item Explain the less ``clear'' parts of your code

\item Give an overview of what to expect when we\\ compile and run
your code

\end{enumerate}

\vspace{\fill}

\end{frame}


\begin{frame}

\frametitle{Conclusion: What To Include In Your Report}

For each task, you should:

\begin{itemize}

\item Give an overview of your submission

\begin{itemize}

\footnotesize

\item What is located where?

\end{itemize}

\item Give a high-level overview of your solution

\begin{itemize}

\footnotesize

\item Use diagrams, pseudo-code, prose, etc.

\item Explain limitations, shortcomings, or additions, if any

\end{itemize}

\item Justify your design decisions

\begin{itemize}

\footnotesize

\item Why this way, and not in some other way?

\end{itemize}

\item Explain the non-trivial parts of your implementation

\begin{itemize}

\footnotesize

\item For example, if you implemented a special data structure

\end{itemize}

\item Explain how to reproduce your test results

\begin{itemize}

\footnotesize

\item How do we compile your code?

\item How do we run your tests?

\item What should we expect to see in case of success, in case of
failure?

\end{itemize}

\end{itemize}

\end{frame}
